\color{blue} On the Synchronization of Computational RFIDs

### 2017-10-25 cover letter/cover.tex
Cover TMC

	With this letter we are submitting an article titled \emph{On the 
		Synchronization 
		of Intermittently Powered Wireless Embedded Systems}.
	The objective of this article is to provide initial observations pertaining to 
	the synchronization of battery-free computational RFID platforms. In 
	particular, we design and implement the first synchronization protocol for the 
	WISP (Wireless 
	Identification and Sensing Platform) and provide real-world experiments, as 
	well as mathematical analysis to evaluate its performance. We also 
	provide an overview of new 
	research opportunities in this emerging domain.

@@

	We believe that \emph{IEEE Transactions on Communications} is 
	the best 
	venue to present our work, as its scope 
	perfectly matches with the scope of our contribution. Thank you in advance for 
	considering our submission.

>>>>

	With this letter we are submitting an article titled \emph{On the Synchronization of Computational RFIDs}.
	The objective of this article is to provide initial observations pertaining to 
	the synchronization of battery-free computational RFID platforms. In 
	particular, we design and implement the first synchronization protocol for the 
	WISP (Wireless 
	Identification and Sensing Platform) and provide real-world experiments, as 
	well as mathematical analysis to evaluate its performance. We also 
	provide an overview of new 
	research opportunities in this emerging domain.

@@

	We believe that \emph{IEEE Transactions on Mobile Computing} is 
	the best 
	venue to present our work, as its scope 
	perfectly matches with the scope of our contribution. Thank you in advance for 
	considering our submission.
